Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-03 papers/03 journal final/appendix.tex
v16
final version

\appendix%[Supplementary Material ]
\subsection{Algorithm 1: Derivation and Convergence Analysis}
\label{app:CA}
The derivation and convergence analysis of Algorithm 1 relies (for the most part) on the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}. The objective of this appendix is to show that the proposed market-clearing game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE, i.e., item (i) of Proposition \ref{prp:conv}. Therefore, we invoke \cite[Theorem~2]{belgioioso2020semi} to prove convergence of Algorithm \ref{alg:alg1}, i.e., item (ii) of Proposition \ref{prp:conv}. For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.

@@

\subsection{Alternating Projection for Operational Feasibility}
\label{APA}
In this appendix, we propose an efficient algorithm to compute the projection onto the set $\mathcal{U}_{N+1}$  (line 30 in Algorithm~\ref{alg:alg1}). First, let us recall the structure of $u_{N+1}$, i.e.,
$$u_{N+1}=\col\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right),$$ and let us define the sets
\begin{align}
	\mc S_1 &:= \{u_{N+1} \mid \text{\eqref{eq:line} and \eqref{eq:grid_ex} hold}\},\\
	%
	\mc S_2 &:= \{u_{N+1} \mid \text{\eqref{eq:pf_p} and \eqref{eq:pf_q} hold}\},
\end{align}
such that $\mathcal{U}_{N+1} = \mc S_1 \cap \mc S_2$. 
%
The proposed method, summarized in Algorithm~\ref{alg:alg2}, is essentially a \textit{Douglas--Rachford splitting} (DRS) \cite[\S~26.3]{bauschke2011convex} applied to the \textit{best approximation problem} $ {\argmin}_{\xi \in \mc S_1 \cap \mc S_2}  \|\xi-u_{N+1}\| =\proj_{\mc S_1 \cap \mc S_2}(u_{N+1}) $, see e.g. \cite[\S~4.3]{bauschke2015projection} for a formal derivation of the algorithm.

>>>>

\appendix%[Supplementary Material ]
\subsection{Algorithm 1: Derivation and Convergence Analysis}
\label{app:CA}
The derivation and convergence analysis of Algorithm 1 relies (for the most part) on the \textit{customized preconditioned proximal-point (cPPP)} algorithm for generalized aggregative games proposed in \cite[Algorithm~6]{belgioioso2020semi}. The objective of this appendix is to show that the proposed market-clearing game \eqref{eq:locOpt}, with cost functions and constraints sets defined in \eqref{eq:cost_def}-\eqref{eq:Cconstr_def}, satisfies all the technical conditions in \cite[Theorem~2]{belgioioso2020semi}, among which is the existence of a variational GNE, i.e., item (i) of Proposition \ref{prp:conv}. Therefore, we invoke \cite[Theorem~2]{belgioioso2020semi} to prove convergence of Algorithm 1, i.e., item (ii) of Proposition \ref{prp:conv}. For a complete convergence analysis of the cPPP algorithm for aggregative games we refer to \cite[Appendix~C]{belgioioso2020semi}.

@@

\subsection{Alternating Projection for Operational Feasibility}
\label{APA}
In this appendix, we propose an efficient algorithm to compute the projection onto the set $\mathcal{U}_{N+1}$  (Algorithm~3~(i)). First, let us recall the structure of $u_{N+1}$, i.e.,
$$u_{N+1}=\col\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right),$$ and let us define the sets
\begin{align}
	\mc S_1 &:= \{u_{N+1} \mid \text{\eqref{eq:line} and \eqref{eq:grid_ex} hold}\},\\
	%
	\mc S_2 &:= \{u_{N+1} \mid \text{\eqref{eq:pf_p} and \eqref{eq:pf_q} hold}\},
\end{align}
such that $\mathcal{U}_{N+1} = \mc S_1 \cap \mc S_2$. 
%
The proposed method, summarized in Algorithm~\ref{alg:alg2}, is essentially a \textit{Douglas--Rachford splitting} (DRS) \cite[\S~26.3]{bauschke2011convex} applied to the \textit{best approximation problem} $ {\argmin}_{\xi \in \mc S_1 \cap \mc S_2}  \|\xi-u_{N+1}\| =\proj_{\mc S_1 \cap \mc S_2}(u_{N+1}) $, see e.g. \cite[\S~4.3]{bauschke2015projection} for a formal derivation of the algorithm.
